Supplementary Information: Global patterns of forest autotrophic carbon fluxes

### 2020-12-18 manuscript/response to reviews.Rmd

**To help clarify the scope of this analysis to readers, we added the following statement to the last paragraph of the introduction: "Our analyses represent a major step forward in relation to previous work [e.g., @luyssaert_co_2007] in that we examine global climatic trends in more variables (9 vs. $\le$ 3), draw from a much larger database (>4 times more records analyzed), and control for the effects of stand age, disturbance, and management."**

Forest C fluxes decreasing with latitude was also not a new finding. The author suggest that it contradicts with some previous studies finding that “net primary productivity of temperate forests rivals that of tropical forests”. However, those high NPP in temperate forests could result from high rates of nitrogen deposition or forest plantation (Yu et al., 2014), which are in different context with the mature, undisturbed forests studied in this manuscript.

**We agree that these results are not surprising to many of us, and state in the introduction that productivity decreases with latitude. Yet, as also noted in the introduction, the form of this relationship is less clear, and contradictory papers have been published in high-profile journals in the last 15 years [@luyssaert_co_2007; @huston_global_2009;  @gillman_latitude_2015]. A crucial part of science is built on high-quality synthesis that clarifies current understanding and probes for unexpected relationships, which is the goal here-- as opposed to testing this as a novel hypothesis.**

**As this comment identifies, results from previous studies were complicated by other effects. The power of this synthesis lies in how it standardises for the effects of stand age and disturbance history, unambiguously clarifying these relationships. We have added text to the introduction to highlight the importance of standardisation of the dataset: "Productivity may vary with stand age, disturbance, and management [@de_lucia_forest_2007; @yu_high_2014; @fernandez-martinez_spatial_2014; @simova_enigma_2017], making clear latitudinal patterns difficult to discern without standardization of the dataset."**

### 2020-12-18 manuscript/appendix.Rmd
fixed up figure legends
@beckybanbury , I couldn't figure out how to insert the "≤" symbol for "p≤0.05", so I just put "p<0.05" (Figs. S4-S9). If you're able to fix that, great.

```
\elandscape
## Figure S1. Sample distribution maps for the nine forest C fluxes analyzed
```{r echo=FALSE, fig.cap = "Figure S1: Maps showing distribution of samples for the nine forest C fluxes analyzed", out.height ='90%', fig.pos='H'}

  knitr::include_graphics("tables_figures/distribution_all_samples.png")
```
\blandscape
## Figure S2. Correlations among climate variables and latitude
```{r echo=FALSE, fig.align = "center", fig.cap = "Figure S2: Scatterplots and Pearson's R values for relationships among climate variables and latitude", out.height='90%', fig.pos='H'}

@@

## Figure S3. Ratios among forest C fluxes as a function of latitude and climate variables
```{r echo=FALSE, fig.align = "center",fig.cap = "Figure S3: Ratios among forest C fluxes as a function of latitude and climate variables. Regressions test variation in allocation to component fluxes for three relationships: (1) $GPP = NPP + R_{auto}$, (2) $NPP = ANPP + BNPP$, and (3) $ANPP = ANPP_{foliage} + ANPP_{stem}$. We interpret analysis of variation in $NPP:R_{auto}$ in the context of CUE (GPP/NPP), as variation in CUE will be directly related to variation in $NPP:R_{auto}$.", out.width ='75%', fig.pos='H'}

  knitr::include_graphics("tables_figures/ratio_grid_plots.png")
```
\elandscape

\blandscape
## Figure S4. Individual plots of forest C fluxes in relation to mean annual climate, part 1
```{r echo=FALSE, fig.cap = "Figure S4: Individual plots of forest C fluxes in relation to mean annual climate, part 1.", out.height='90%', fig.pos='H'}

@@

\newpage
## Figure S5. Individual plots of forest C fluxes in relation to mean annual climate, part 2
```{r echo=FALSE, fig.cap = "Figure S5: Individual plots of forest C fluxes in relation to mean annual climate, part 2.", out.height='90%', fig.pos='H'}

@@

## Figure S6. Individual plots of forest C fluxes in relation to mean climate seasonality, part 1
```{r echo=FALSE, fig.cap = "Figure S6: Individual plots of forest C fluxes in relation to mean climate seasonality, part 1.", out.height ='80%', fig.pos='H'}

@@

\newpage
## Figure S7. Individual plots of forest C fluxes in relation to mean climate seasonality, part 2
```{r echo=FALSE, fig.cap = "Figure S7: Individual plots of forest C fluxes in relation to mean climate seasonality, part 2.", out.width ='80%', fig.pos='H'}

@@

\newpage
## Figure S8. Growing season length-standardized forest C fluxes in relation to mean growing season climate, part 1
```{r echo=FALSE, fig.cap = "Figure S8: Growing season length-standardized forest C fluxes in relation to mean growing season climate, part 1.", out.width ='95%', fig.pos='H'}

@@

\newpage
## Figure S9. Growing season length-standardized forest C fluxes in relation to mean growing season climate, part 2
```{r echo=FALSE, fig.cap = "Figure S9: Growing season length-standardized forest C fluxes in relation to mean growing season climate, part 2.", out.width ='95%', fig.pos='H'}

>>>>

```
\elandscape
## Figure S1. Sample distribution maps for the nine forest C fluxes analyzed
```{r echo=FALSE, fig.cap = "Figure S1: Maps showing distribution of samples for the nine forest C fluxes analyzed. Variables are defined in Table 2.", out.height ='90%', fig.pos='H'}

  knitr::include_graphics("tables_figures/distribution_all_samples.png")
```
\blandscape
## Figure S2. Correlations among climate variables and latitude
```{r echo=FALSE, fig.align = "center", fig.cap = "Figure S2: Scatterplots and Pearson's R values for relationships among climate variables and latitude. Climate variables are as defined in Table S1.", out.height='90%', fig.pos='H'}

@@

## Figure S3. Ratios among forest C fluxes as a function of latitude and climate variables
```{r echo=FALSE, fig.align = "center",fig.cap = "Figure S3: Ratios among forest C fluxes as a function of latitude and climate variables. Regressions test variation in allocation to component fluxes for three relationships: (1) $GPP = NPP + R_{auto}$, (2) $NPP = ANPP + BNPP$, and (3) $ANPP = ANPP_{foliage} + ANPP_{stem}$. We interpret analysis of variation in $NPP:R_{auto}$ in the context of CUE ($CUE = NPP/GPP = NPP/(NPP+R_auto)$), as variation in CUE will be directly related to variation in $NPP:R_{auto}$. All relationships are non-signficant (p>0.05).", out.width ='80%', fig.pos='H'}

  knitr::include_graphics("tables_figures/ratio_grid_plots_nolegend.png")
```
\elandscape

\blandscape
## Figure S4. Individual plots of forest C fluxes in relation to mean annual climate, part 1
```{r echo=FALSE, fig.cap = "Figure S4: Individual plots of forest C fluxes in relation to mean annual climate, part 1. Statistical signficance is indicated by solid (p < 0.05) and dashed (p > 0.05) regression lines. Fits shown are of the form with the lowest AIC for each C variable- climate variable combination (Table S2).", out.height='85%', fig.pos='H'}

@@

\newpage
## Figure S5. Individual plots of forest C fluxes in relation to mean annual climate, part 2
```{r echo=FALSE, fig.cap = "Figure S5: Individual plots of forest C fluxes in relation to mean annual climate, part 2. Statistical signficance is indicated by solid (p < 0.05) and dashed (p > 0.05) regression lines. Fits shown are of the form with the lowest AIC for each C variable- climate variable combination (Table S2).", out.height='85%', fig.pos='H'}

@@

## Figure S6. Individual plots of forest C fluxes in relation to mean climate seasonality, part 1
```{r echo=FALSE, fig.cap = "Figure S6: Individual plots of forest C fluxes in relation to mean climate seasonality, part 1. Statistical signficance is indicated by solid (p < 0.05) and dashed (p > 0.05) regression lines. Fits shown are of the form with the lowest AIC for each C variable- climate variable combination (Table S2).", out.height ='80%', fig.pos='H'}

@@

\newpage
## Figure S7. Individual plots of forest C fluxes in relation to mean climate seasonality, part 2
```{r echo=FALSE, fig.cap = "Figure S7: Individual plots of forest C fluxes in relation to mean climate seasonality, part 2. Statistical signficance is indicated by solid (p < 0.05) and dashed (p > 0.05) regression lines. Fits shown are of the form with the lowest AIC for each C variable- climate variable combination (Table S2).", out.width ='80%', fig.pos='H'}

@@

\newpage
## Figure S8. Growing season length-standardized forest C fluxes in relation to mean growing season climate, part 1
```{r echo=FALSE, fig.cap = "Figure S8: Growing season length-standardized forest C fluxes in relation to mean growing season climate, part 1. Statistical signficance is indicated by solid (p < 0.05) and dashed (p > 0.05) regression lines.", out.width ='95%', fig.pos='H'}

@@

\newpage
## Figure S9. Growing season length-standardized forest C fluxes in relation to mean growing season climate, part 2
```{r echo=FALSE, fig.cap = "Figure S9: Growing season length-standardized forest C fluxes in relation to mean growing season climate, part 2. Statistical signficance is indicated by solid (p < 0.05) and dashed (p > 0.05) regression lines.", out.width ='95%', fig.pos='H'}
